---
title: 'Get started'
---

```{r, message=FALSE}
library(campsis)
```

## Load model

Load a PK model from the built-in model library or load your own one.

```{r}
model <- model_suite$nonmem$advan4_trans4 # 2-compartment PK model with absorption compartment
```

## Create dataset

Create a dataset of 10 individuals in Campsis For instance, let's give 1000 mg QD for 3 days and observe every hour.

```{r}
dataset <- Dataset(10) %>%
  add(Bolus(time=0, amount=1000, ii=24, addl=2)) %>%
  add(Observations(times=0:72))
```

## Simulate

Simulate this very simple protocol:

```{r, include=FALSE}
results <- model %>% simulate(dataset, seed=1)
head(results)
```

## Plot results

Plot all simulated profiles using a spaghetti plot:

```{r get_started_spaguetti_plot, fig.align='center', fig.height=4, fig.width=8}
spaghettiPlot(results, "CP")
```

Or use a shaded plot to see the simulated 90% prediction interval:

```{r get_started_shaded_plot, fig.align='center', fig.height=4, fig.width=8}
shadedPlot(results, "CP")
```

## Simulate arms

The dataset can contain more than one treatment arm. In the example below, we explicitly create two arms. The first arm receives a dose of 1000 mg QD, while the second arm receives twice this dose amount.

```{r get_started_2arms_plot, fig.align='center', fig.height=4, fig.width=8, results='hide', message=FALSE}
arm1 <- Arm(subjects=50, label="1000 mg QD") %>%
  add(Bolus(time=0, amount=1000, ii=24, addl=2)) %>%
  add(Observations(times=0:72))

arm2 <- Arm(subjects=50, label="2000 mg QD") %>%
  add(Bolus(time=0, amount=2000, ii=24, addl=2)) %>%
  add(Observations(times=0:72))

dataset <- Dataset() %>%
  add(c(arm1, arm2))

results <- model %>% simulate(dataset, seed=1)
shadedPlot(results, "CP",  colour="ARM")
```

## Derive from base model

Scenarios derived from the base model and/or dataset can be easily implemented. Below, we'd like to see what happens if the clearance of this model is multiplied by two.

```{r get_started_2arms_scenarios_plot, fig.align='center', fig.height=4, fig.width=8, results='hide', message=FALSE}
scenarios <- Scenarios() %>%
  add(Scenario("Base model")) %>% # Original CL is 5
  add(Scenario("Increased clearance", model=~.x %>% replace(Theta(name="CL", value=10))))

results <- model %>% simulate(dataset, scenarios=scenarios, seed=1)
shadedPlot(results, "CP", colour=c("ARM"), strat_extra="SCENARIO") + ggplot2::facet_wrap(~SCENARIO)
```