---
title: 'Get started'
---

```{r, message=FALSE}
library(campsis)
```

## Load model

Load a PK model from the built-in model library or load your own one.

```{r}
model <- model_suite$nonmem$advan4_trans4 # 2-compartment PK model with absorption compartment
```

## Create dataset

Create a dataset of 10 individuals in Campsis For instance, let's give 1000 mg QD for 3 days and observe every hour.

```{r}
dataset <- Dataset(10) %>%
  add(Bolus(time=0, amount=1000, ii=24, addl=2)) %>%
  add(Observations(times=0:72))
```

## Simulate

Simulate this very simple protocol:

```{r}
results <- model %>% simulate(dataset, seed=1)
head(results)
```

## Plot results

Plot all simulated profiles using a spaghetti plot:

```{r get_started_spaguetti_plot, fig.align='center', fig.height=4, fig.width=8}
spaghettiPlot(results, "CONC") +
  ggplot2::theme_bw()
```

Or use a shaded plot to see the simulated 90% prediction interval:

```{r get_started_shaded_plot, fig.align='center', fig.height=4, fig.width=8}
shadedPlot(results, "CONC") +
  ggplot2::theme_bw()
```

## Simulate arms

The dataset can contain more than one treatment arm. In the example below, we explicitly create two arms. The first arm receives a dose of 1000 mg QD, while the second arm receives twice this dose amount.

```{r get_started_2arms_plot, fig.align='center', fig.height=4, fig.width=8, results='hide', message=FALSE}
arm1 <- Arm(subjects=50, label="1000 mg QD") %>%
  add(Bolus(time=0, amount=1000, ii=24, addl=2)) %>%
  add(Observations(times=0:72))

arm2 <- Arm(subjects=50, label="2000 mg QD") %>%
  add(Bolus(time=0, amount=2000, ii=24, addl=2)) %>%
  add(Observations(times=0:72))

dataset <- Dataset() %>%
  add(c(arm1, arm2))

results <- model %>% simulate(dataset, seed=1)
shadedPlot(results, "CONC",  colour="ARM") +
  ggplot2::theme_bw()
```

## Derive from base model

Scenarios derived from the base model and/or dataset can be easily implemented. Below, we'd like to see what happens if the clearance of this model is multiplied by two.

```{r get_started_2arms_scenarios_plot, fig.align='center', fig.height=4, fig.width=8, results='hide', message=FALSE}
scenarios <- Scenarios() %>%
  add(Scenario("Base model")) %>% # Original CL is 5
  add(Scenario("Increased clearance", model=~.x %>% replace(Theta(name="CL", value=10))))

results <- model %>% simulate(dataset, scenarios=scenarios, seed=1)
shadedPlot(results, "CONC", colour=c("ARM"), strat_extra="SCENARIO") +
  ggplot2::facet_wrap(~SCENARIO) +
  ggplot2::theme_bw()
```

## Post-process your results

For instance, let's derive some non-compartmental analysis (NCA) metrics at Day 3, for each scenario and arm, with the [`campsisnca`](https://github.com/Calvagone/campsisnca) package:

```{r get_started_post_processing, message=FALSE}
library(campsisnca)
library(gtsummary)
library(gt)

table <- NCAMetricsTable()

for (scenario in c("Base model", "Increased clearance")) {
  for (arm in c("1000 mg QD", "2000 mg QD")) {
    data <- results %>% dplyr::filter(SCENARIO==scenario, ARM==arm) %>% timerange(48, 72, rebase=TRUE)
    
    nca <- NCAMetrics(x=data, variable="CONC", scenario=c(scenario=scenario, arm=arm)) %>%
      add(c(AUC(unit="ng/mL*h"), Cmax(unit="ng/mL"), Tmax(unit="h"), Ctrough(unit="ng/mL"))) %>%
      calculate()
    
    table <- table %>%
      add(nca)
  }
}
table %>%
  export(dest="gt", subscripts=TRUE, combine_with="tbl_merge")
```

We invite you to check out how [e-Campsis](https://www.youtube.com/embed/3YPIeQEdQng?si=PugvJ1oI_Hb5CbPm) can help you derive the NCA metrics in a more automated and user-friendly way.
