---
title: 'Installation'
---

## Preliminaries

* Download and install latest version of [R](https://cran.r-project.org/bin/windows/base/)
* Download and install [R tools](https://cran.r-project.org/bin/windows/Rtools/)

## Install the Campsis suite

Installing the Campsis suite is easy. First download our Campsis package manager using `remotes`:

```{r, eval=FALSE}
remotes::install_github("Calvagone/campsisverse")
```

Then, run the install method. This will install all the packages of the suite, including their dependencies and the simulation engines (`mrgsolve` and `rxode2`).
Follow the instructions in the console.

```{r, eval=FALSE}
campsisverse::install()
```

## Qualify the Campsis suite

You want to qualify your suite? We have everything you need.  
Please contact [Calvagone](mailto:campsis@calvagone.com) to get your certificate and qualification suite of models.  
Thanks to our [`campsisqual`](https://github.com/Calvagone/campsisqual) package, an extensive IQ/OQ report can be issued. Please visit our [Quality tab](./quality.html).  

